---
title: "Organising records for full text screening"
author: "James Orr"
output:
   html_notebook:
     code_folding: hide
     theme: flatly
     toc: true
     toc_depth: 4
     number_sections: no
---

*Introduction*

Here I'll combine the records collected from previous reviews with the papers found during ASReview to create a dataset that I can then use for full text screening and data extraction.

```{r, echo=TRUE, results='hide'}
#### Clear  environment 
rm(list = ls())         

#### Required packages
library(tidyverse)        # for general use
library(readxl)           # to read xls files

```

*Load xlsx files*

```{r}
previous <- read_excel("from-previous-reviews.xlsx")
asreview_results <- read_excel("asreview_outputs.xlsx")
```

*Organise data*

```{r}
asreview_results <- asreview_results %>%
  filter(included == "1") %>%
  select(c(Authors, Title, `Source Title`, Abstract, `Publication Year`,
           DOI, `UT (Unique WOS ID)`))

previous <- previous %>%
  rename(Title = `Article Title`) %>%
  mutate(`UT (Unique WOS ID)` = NA)

previous_yes <- filter(previous, Included == "yes") 
previous_no <- filter(previous, Included == "no") 

previous_yes <- previous_yes %>%
  select(-c(Authors, Title, `Source Title`, Abstract, `Publication Year`,
            `UT (Unique WOS ID)`))
```

*Merge data*

All of the previous records that had "Included" = "yes" were in the asreview list, so that makes joining a bit easier 

```{r}
full_text_screening <- left_join(asreview_results, previous_yes, by = "DOI")
full_text_screening <- full_text_screening %>%
  mutate(asreview = 1,
         previous = if_else(Included == "yes", 1, 0))
full_text_screening$previous[is.na(full_text_screening$previous)] <- 0

previous_no$asreview = 0
previous_no$previous = 1

full_text_screening <- bind_rows(full_text_screening, previous_no)
```

*Confirm there are no duplicates*

```{r}
length(unique(full_text_screening$DOI))
```

*Reorder and save*

```{r}
full_text_screening <- full_text_screening %>%
  arrange(desc(previous), desc(asreview), desc(`Publication Year`))

#write.csv(full_text_screening, "full_text_screening.csv", row.names = F)
```

