---
title: "Organising WoS search results"
author: "James Orr"
output:
   html_notebook:
     code_folding: hide
     theme: flatly
     toc: true
     toc_depth: 4
     number_sections: no
---

### Introduction

Web of Science only allows export of 1000 records at a time. Here I am compiling many of these 1000 groups of records together so they can be organised easily. 

```{r, echo=TRUE, results='hide'}
#### Clear  environment 
rm(list = ls())         

#### Required packages
library(tidyverse)        # for general use
library(readxl)           # to read xls files
library(data.table)       # to split into many csv files

```


### Load all xls files into one R object

```{r}
# Get a list of all .xls files in the folder
file_list <- list.files(pattern = "*.xls", full.names = TRUE)

# Read all .xls files into a single data frame
WoS_results <- map_df(file_list, ~ read_excel(.x, col_types = "text"))

rm(file_list)
```


### Must be in English 

```{r}
#WoS_results_NE <- WoS_results %>%
#  filter(Language != "English")
```

Don't need to do anything - records that were labelled as not being in English did have English abstracts in WoS so can be included in the ASReview process

### Select relevant variables 

```{r}
WoS_results <- WoS_results %>%
   select(c("Authors",
            "Article Title",
            "Source Title",
            "Abstract",
            "Publication Year",
            "Early Access Date",
            "DOI",
            "UT (Unique WOS ID)")) %>%
   arrange(desc(`Publication Year`))

WoS_results <- rename(WoS_results, Title = `Article Title`)
```

### Separate out the papers with missing abstracts

```{r}
missing_abstract <- WoS_results %>%
  filter(is.na(Abstract))

abstract_screening_input <- WoS_results %>%
  filter(!is.na(Abstract))
```


### Save full sheet

```{r}
write.csv(abstract_screening_input, "abstract_screening_input.csv", row.names=F)
write.csv(missing_abstract, "missing_abstract.csv", row.names=F)

```


